R Notebook

### 2020-12-11 AdvendOfCode2020/draft_post_3.Rmd
Day 07 part 2

>>>>

```{r}

# transforms the bag rules into a graph from bag to contains
bag.graph <- bag.rules %>% 
  transmute( from = paste0(bag.type,"_",bag.color),
             to = paste0(ctn.bag.type,"_",ctn.bag.color),
             weight = ctn.bag.qtd ) %>% 
  filter(weight!=0) %>% 
  # keep the capacity (as weight) and directed
  as_tbl_graph(bag.graph, directed = T)

# finds all paths starting 
paths <- bag.graph %>% 
  all_simple_paths(from = "shiny_gold")

# for each path gets the weight between the nodes
paths %>% 
  map_dbl(function(.p, .bg){
    # run through the path
    weights <- vector(mode="double", (length(.p)-1))
    for (i in 1:(length(.p)-1)){
      # gets the weights along the pagh
      weights[i] <- .bg %>% 
        filter( from == .p[i], 
                to   == .p[i+1]) %>% 
        pull(weight)
    }
    # return the product of the weights
    return(prod(weights))
  }, .bg=activate(bag.graph, edges)) %>% 
  # sum them up
  sum()

```
